Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
New file

@@

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-amaxb,-0.1, 0, 0.1, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-1.05*amaxb, 1.05*amaxb),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(0,0,0,0,"pt"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

    plot.alpha.diversity.gtable <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
    plot.alpha.diversity.legend <- legend_extractor(plot.alpha.diversity.gtable)
    plot.alpha.diversity.yaxis <- plot.alpha.diversity.gtable$grobs[[3]]

    plot.alpha.diversity <- plot.alpha.diversity +
        theme(legend.position = "none",
              axis.text.x = element_blank(),
              axis.text.y=element_blank())

    plot.gtable.alpha.diversity.stripped <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
    return(list(plot = plot.gtable.alpha.diversity.stripped$grobs[[6]],
                yaxis = plot.alpha.diversity.yaxis,
                xaxis = plot.alpha.diversity.gtable$grobs[[7]],
                legend = plot.alpha.diversity.legend))
}

@@

```{r alphabeta beta}
plot.beta <- function(diversity, fig.permar2.text = "R2 of variable \nin Bray-Curtis distance", fig.textsize = 15) {
    plot.beta.diversity <- ggplot(diversity, aes(x = reorder(Name, R2), y= R2)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        theme_classic(fig.textsize) +
        ylab(fig.permar2.text) +
        theme(axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"),
              legend.position="right",
              legend.direction="vertical",
              legend.box.margin=margin(0,0,0,0,"pt"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              legend.title.align = 0,
              legend.text.align = 0)

    plot.gtable.beta.diversity <- ggplot_gtable(ggplot_build(plot.beta.diversity))
    plot.xlab.beta.diversity <- xlabb_extractor(plot.gtable.beta.diversity)

    plot.beta.diversity <- plot.beta.diversity  +
        theme(axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x  =  element_blank(),
              axis.title.y = element_blank(),
              legend.position = "none")
    plot.gtable.beta.diversity.stripped <- ggplot_gtable(ggplot_build(plot.beta.diversity))

      return(list(plot =plot.gtable.beta.diversity.stripped$grobs[[6]],
                xaxis = plot.gtable.beta.diversity$grobs[[7]]))
}
```

g4 <- arrangeGrob(grobs = gs4,
            layout_matrix = rbind(
                c(1,    2,    3, 4),
                c(NA, 5,    6, NA),
                c(NA, NA, 7, NA)),
            widths=c(4, 0.7, 5, 5),
            heights=c(10, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)
```

>>>>

### Plot functions

```{r EdgeR functions, code=readLines("aaro/edgeR_plot_functions.R")}
source("articletwo-ggplot.R")
```

@@

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(1,    2,    3, NA, 4),
                      c(1,    2,    3, NA, NA),
                      c(NA, 5,    6, NA, NA),
                      c(NA, NA, 7, NA, NA)),
                  widths=c(4, 0.7, 5, 0.7, 4),
            heights=c(3, 7, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

@@
